\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
little things in sec 1

%=============================================================================
\paragraph*{Related Works}
%=============================================================================

The reducer commutativity problem can be reduced to a \emph{program equivalence}
problem. One creates another program $R'$ that first non-deterministically swaps
two consecutive input values and then executes the code of $R$. If $R'$ and $R$
are equivalent, using the fact that all permutations of a list can be obtained
by swapping consecutive list elements finitely many times\footnote{Here is an
example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive
elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$
[2;\textbf{1};\textbf{3};4;5] $\rightarrow$
[2;3;1;\textbf{4};\textbf{5}]$\rightarrow$
[2;3;\textbf{1};\textbf{5};4]$\rightarrow$
[\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
be commutative. There is a series of research results on program equivalence
checking (or closely related topics such as regression verification and
translation validation): c.f.,
\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
to name a few.

From a high-level view, checking equivalence of two programs $P$ and $P'$ can be
reduced to a sequential verification problem by executing $P'$ after $P$,
followed by checking whether the two programs always produce the same outputs.
The approach can be made more efficient by finding the
right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an
interleaved manner. A lot of research effort in this direction is in finding
good synchronization points. In this work, we propose the \emph{head of the
top-level reducer loop} as the synchronization point suitable for reducer
commutativity analysis. According to our experience discussed later on, the
reducers usually contain just a single such loop. Moreover, for the case when
there are more top-level loops in a reducer, we propose a way of breaking such a
reducer into several ones to be checked independently.

However, in our experience, if one naively reduces the commutativity problem to
an equivalence problem and checks it in a precise manner, many reducers cannot
be verified. Therefore, J-ReCoVer uses an over-approximation of the reducer's
behaviour. This approximation allows for a much more efficient, yet---according
to our experiments---precise enough commutativity analysis.

@@

Various forms of sequentialisation are behind further research works too, such
as, e.g., works dealing with the concept of \emph{robustness} of event-driven
asynchronous programs~\cite{ahmed2017:robustness} or those dealing with programs
running under some \emph{relaxed memory
models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
computation models are again quite different from that of reducers, and hence
the results cannot be directly applied.
Besides verification, another interesting research direction is the
\emph{synthesis} of MapReduce programs~\cite{SmithA16}. Commutativity analysis
is used as a component under the synthesis framework.

@@

%-----------------------------------------------------------------------------
\paragraph{A note on dealing with output in the main loop.} 
%-----------------------------------------------------------------------------

So far we have assumed that there was no output in the main loop and mentioned
that this restriction is lifted in J-ReCoVer. Due to space restrictions, a
proper explanation of the way of handling this issue is beyond the scope of this
paper, but we give at least a brief sketch of the solution. In particular, the
Preprocessor performs one more transformation which adds an assignment $v := e$
for every $out(e)$ statement in the main loop where $v$ is a fresh variable
assigned just once in the loop body. This makes the output visible for our
analysis since $v$ appears in Formula~\ref{eq:commu}. The Prover then makes an
additional check whether the value of $F(n, x_1,x_2,\ldots,x_k)$ projected on
$v$ stays the same for any input value $n$ and any initial values of the
variables $x_i$.

>>>>

%=============================================================================
\paragraph*{Related Work.}
%=============================================================================

The reducer commutativity problem can be reduced to a \emph{program equivalence}
problem. One creates another program $R'$ that first non-deterministically swaps
two consecutive input values and then executes the code of $R$. If $R'$ and $R$
are equivalent, using the fact that all permutations of a list can be obtained
by swapping consecutive list elements finitely many times\footnote{Here is an
example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive
elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$
[2;\textbf{1};\textbf{3};4;5] $\rightarrow$
[2;3;1;\textbf{4};\textbf{5}]$\rightarrow$
[2;3;\textbf{1};\textbf{5};4]$\rightarrow$
[\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
be commutative. A series of research works address program equivalence
checking (or closely related topics such as regression verification and
translation validation), cf.
\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
to name a few.

From a high-level view, checking equivalence of two programs $P$ and $P'$ can be
reduced to a sequential verification problem by executing $P'$ after $P$,
followed by checking whether the two programs always produce the same outputs.
The approach can be made more efficient by finding the
right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an
interleaved manner. A lot of research effort have been invested into finding
good synchronization points. In this work, we propose the \emph{head of the
top-level reducer loop} as the synchronization point suitable for reducer
commutativity analysis. According to our experience, discussed later on, the
reducers usually contain just a single such loop. Moreover, for the case when
there are more top-level loops in a reducer, we propose a way of breaking the 
reducer into several ones to be checked independently.

However, we observe that if one naively reduces the commutativity problem to
an equivalence problem and checks it in a precise manner, many reducers cannot
be verified. Therefore, J-ReCoVer uses an over-approximation of the reducer's
behaviour. This approximation allows for a much more efficient, yet---according
to our experiments---precise enough commutativity analysis.

@@

%Various forms of sequentialisation are behind further research works too, 
Various forms of sequentialisation are also used in works dealing with the concept 
of \emph{robustness} of event-driven
asynchronous programs~\cite{ahmed2017:robustness} or works dealing with programs
running under some \emph{relaxed memory
models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
computation models are again quite different from that of reducers, and
their results cannot be directly applied.
Besides verification, another interesting research direction is the
\emph{synthesis} of MapReduce programs~\cite{SmithA16}, which uses commutativity analysis
as a component of its framework.

@@
